A Classical Density-Functional Theory for Describing Water Interfaces

### 2012-05-29 papers/water-SAFT/paper.tex

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{figs/density-single-rod}
\end{center}
\caption{ Density profiles for a single rod of different radii. The dotted line
represents the saturated liquid density and the points represent the
expected contact density derived from the contact value theorem and
data used in Figure \ref{fig:energy-vs-diameter}.}
\label{fig:density-single-rod}
\end{figure}

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{figs/density-single-rod}
\end{center}
\caption{ Density profiles for a single rod of different radii. The dotted line
represents the saturated liquid density and the points represent the
expected contact density derived from the contact value theorem and
the free energy data
data plotted in Figure \ref{fig:energy-vs-diameter}.}
\label{fig:density-single-rod}
\end{figure}
